---
output:
  html_document: default
  pdf_document: default
---

Samuel Li
scl2567



#Problem 1.

```{r echo=FALSE}
library(ggplot2)

#A
profs <- read.csv("profs.csv")
ggplot(profs, aes(x = eval)) +
  geom_histogram(binwidth = 0.2, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Course Evaluation Scores",x = "Evaluation Score",y = "Frequency") +
  theme_minimal()
```
In this plot, it is skewed to the left, with a mean and median at around 4

```{r echo=FALSE}

#B
ggplot(profs, aes(x = native, y = eval, fill = native)) +
  geom_boxplot() +
  labs(title = "Course Evaluation Scores by Native English Speaker Status", x = "Native English Speaker", y = "Evaluation Score") +
  theme_minimal()

```
In this plot, the non native speaker scores are on average lower than the native speakers.




```{r echo=FALSE}





#C
ggplot(profs, aes(x = eval)) +
  geom_histogram(binwidth = 0.5, fill = "skyblue", color = "black") +
  facet_grid(rows = vars(gender)) +  # Creates separate plots for male and female
  labs(title = "Distribution of Course Evaluation Scores by Gender", x = "Evaluation Score", y = "Frequency") +
  theme_minimal()
```
This plot reveals that the male scores are slightly on average higher than the female ones. 

```{r echo=FALSE}







#D
ggplot(profs, aes(x = beauty, y = eval)) +
  geom_point(color = "blue") +
  geom_smooth(method = "lm", color = "red", se = FALSE) +  
  labs(title = "Relationship Between Physical Attractiveness and Course Evaluations", x = "Physical Attractiveness Score", y = "Evaluation Score") +
  theme_minimal()
```
There is a positive weak correlation between physical attractiveness and evaluation score. 




#Problem 2.
```{r echo=FALSE}
#A
library(ggplot2)
library(dplyr)

bikeshare <- read.csv("bikeshare.csv")

bikeshare$average_rentals <- ave(bikeshare$total, bikeshare$hr, FUN = mean)

ggplot(bikeshare, aes(x = hr, y = average_rentals)) +
  geom_line() + labs(x = "Hour of the Day", y = "Average Number of Bike Rentals", title = "Average Number of Bike Rentals per Hour of the Day")
```

```{r echo=FALSE}
#B
library(ggplot2)
library(dplyr)

bikeshare <- read.csv("bikeshare.csv")

bikeshare$avg_rentals <- ave(bikeshare$total, bikeshare$hr, bikeshare$workingday, FUN = mean)

# Create the line plot with facets for working vs. non-working days
ggplot(bikeshare, aes(x = hr, y = avg_rentals)) +
  geom_line() +
  labs(x = "Hour of the Day", y = "Average Number of Bike Rentals", title = "Average Number of Bike Rentals per Hour of the Day") +
  facet_wrap(~workingday)
```
These plots show the average number of bike rentals per Hour of the day based on whether it is a working day or not. As seen, working days tend to see a spike on the start and end hours of the usual working day shift(9-5). However, when it is not a working day, the rentals seem to be higher in the afternoon. 

```{r echo=FALSE}
#C
library(ggplot2)
library(dplyr)

bikeshare <- read.csv("bikeshare.csv")

bike_9am <- subset(bikeshare, hr == 9)

bike_9am_summary <- aggregate(total ~ weathersit + workingday, data = bike_9am, FUN = mean)

colnames(bike_9am_summary)[3] <- "avg_ridership"

ggplot(bike_9am_summary, aes(x = factor(weathersit), y = avg_ridership)) +
  geom_col() + labs(x = "Weather Condition", y = "Average Number of Bike Rentals", title = "Average Ridership during the 9AM Hour") +
  facet_wrap(~workingday)
```
This is a faceted bar plot of whether it is a working day or not that displays the average ridership in different weather conditions at 9am.





#Problem 3.
```{r echo=FALSE}
capmetro_UT <- read.csv("capmetro_UT.csv")
capmetro_UT = mutate(capmetro_UT, day_of_week = factor(day_of_week, levels=c("Mon", "Tue", "Wed","Thu", "Fri", "Sat", "Sun")), month = factor(month, levels=c("Sep", "Oct","Nov")))
```

```{r echo=FALSE}
#1

capmetro_average_boardings <- capmetro_UT %>%
  group_by(hour_of_day, day_of_week, month) %>%
  summarize(avg_boardings = mean(boarding), .groups="keep")

  
ggplot(capmetro_average_boardings) + geom_line(aes(x=hour_of_day, y = avg_boardings, color = month)) + labs(x="Hour of the Day", y="Average Boardings", title="average boardings by hour of the day, day of week, and month.") + facet_wrap(~day_of_week) 
```

```{r echo=FALSE}
#2
ggplot(capmetro_UT) + geom_point(aes(x = temperature, y = boarding, color = weekend )) + labs(x="Temperature", y="Boardings", title="scatter plot of temperature vs boardings") + facet_wrap(~hour_of_day)
```






#Problem 4.
```{r echo=FALSE}
#A
library(dplyr)
library(ggplot2)
library(knitr)
billboard <- read.csv("billboard.csv")

top_songs <- aggregate(weeks_on_chart ~ performer + song, data = billboard, sum, na.rm = TRUE)

top_songs <- top_songs[rank(-top_songs$weeks_on_chart) <= 10, ]

library(knitr)
kable(top_songs, col.names = c("Performer", "Song", "Total Weeks"), 
      caption = "Top 10 Most Popular Songs Since 1958")


```


```{r echo=FALSE}
#B
billboard_filtered <- billboard[billboard$year > 1958 & billboard$year < 2021, ]

unique_songs_count <- tapply(billboard_filtered$song, billboard_filtered$year, unique)

unique_songs_count <- sapply(unique_songs_count, length)

unique_songs_per_year <- data.frame(year = as.numeric(names(unique_songs_count)), 
                                    unique_songs = unique_songs_count)


ggplot(unique_songs_per_year, aes(x = year, y = unique_songs)) +
  geom_line(color = "lightblue") +
  geom_point(color = "grey") +
  labs(
    title = "Musical Diversity of the Billboard Top 100 Over Time",
    x = "Year",
    y = "Number of Unique Songs"
  ) +
  theme_minimal()


```


```{r echo=FALSE}
#C
ten_week_hits <- billboard[billboard$weeks_on_chart >= 10, ]

ten_week_hits_count <- aggregate(song ~ performer, data = ten_week_hits, FUN = function(x) length(unique(x)))

colnames(ten_week_hits_count) <- c("performer", "ten_week_hits")

top_artists <- ten_week_hits_count[ten_week_hits_count$ten_week_hits >= 30, ]

top_artists <- top_artists[order(top_artists$ten_week_hits, decreasing = TRUE), ]

ggplot(top_artists, aes(x = reorder(performer, ten_week_hits), y = ten_week_hits)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip()+
  labs(
    title = "Top 19 Artists with At Least 30 Ten-Week Hits in Billboard Top 100",
    x = "Performer",
    y = "Number of Ten-Week Hits"
  ) +
  theme_minimal()


```
